Towards Practical First-Order Model Counting

### 2025-01-20 doc/paper/paper.tex
Done with Section 2 for now

\todo[inline,caption={}]{
  \begin{itemize}
    \item Adjust the introduction to the new structure (with more subsections)
    \item If I need more space elsewhere, shortening the preliminaries to two
          pages could work (I could expand the introduction by 0.5 page)
  \end{itemize}
}

@@

\todo[inline]{Make sure the distinction between function definitions and
  equations is clear.}

@@

In this paper, we use both logical and algebraic constructs. While the rest of
\cref{sec:preliminaries} focused on the former, this section describes the
latter. We write $\expr{}$ for an arbitrary algebraic expression. In the context
of algebra, a \emph{constant} is a non-negative integer. Likewise, a
\emph{variable} can either be a parameter of a function or a variable introduced
through summation, such as $i$ in the expression $\sum_{i=1}^{n} \expr$. A
\emph{function call} is $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short),
where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
consisting of variables and constants. A (function) \emph{signature} is function
call that contains only variables. Given two function calls $f(\mathbf{x})$ and
$f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches} $f(\mathbf{x})$ if
$x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$. An \emph{equation}
is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.

@@

\todo[inline]{Somewhere: Recall that each equation is either the definition (did
  I define what a definition is?) of a function or the definition of a base case
  of a function. (I could put this in the preliminaries as definitions and then
  reference them below)}

>>>>

\todo[inline,caption={}]{
  \begin{itemize}
    \item If I need more space elsewhere, shortening the preliminaries to two
          pages (perhaps skipping Section 2.2 altogether?)
    \item Adjust the introductory paragraph below to the new structure (with
          more subsections)
  \end{itemize}
}

@@

@@

In this paper, we use both logical and algebraic constructs. While the rest of
\cref{sec:preliminaries} focused on the former, this section describes the
latter. We write $\expr{}$ for an arbitrary algebraic expression. In the context
of algebra, a \emph{constant} is a non-negative integer. Likewise, a
\emph{variable} can either be a parameter of a function or a variable introduced
through summation, such as $i$ in the expression $\sum_{i=1}^{n} \expr$. A
\emph{function call} is $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short),
where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
consisting of variables and constants. A (function) \emph{signature} is function
call that contains only variables. Given two function calls $f(\mathbf{x})$ and
$f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches} $f(\mathbf{x})$ if
$x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$. An \emph{equation}
is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a function call.

@@
